---
title: "LP in R"
author: "Franklin Ngochi"
date: "2023-09-24"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load the lpSolve library
```{r}
library(lpSolve)
```


# Define the coefficients of the objective function
```{r}
objective_coef <- c(420, 360, 300)
```

#Define the right-hand side of capacity constraints
```{r}
rhs_capacity <- c(750, 900, 450)
```

# Define the coefficients for capacity constraints
```{r}
coeff_capacity <- matrix(c(1, 1, 1, 1, 1, 1, 1, 1, 1), nrow = 3, byrow = TRUE)
```

# Define the right-hand side of storage space constraints
```{r}
rhs_storage <- c(13000, 12000, 5000)
```

# Define the coefficients for storage space constraints
```{r}
coeff_storage <- matrix(c(20, 15, 12, 20, 15, 12, 20, 15, 12), nrow = 3, byrow = TRUE)
```

# Define the coefficients for same capacity percentage constraints
```{r}
coeff_percentage <- matrix(c(900, -750, 0, 0, 450, -900), nrow = 2, byrow = TRUE)
```

# Define the direction of optimization (maximization)
```{r}
direction <- "max"
```


# Create the LP model
```{r}
lp_model <- make.lp(0, length(objective_coef))
set.objfn(lp_model, objective_coef)
lp.control(lp_model, sense = direction)
```

#Add capacity constraint
```{r}
for (i in 1:3) {
  add.constraint(lp_model, coeff_capacity[i, ], "<=", rhs_capacity[i])
}
```

#Add storage space constraint
```{r}
for (i in 1:3) {
  add.constraint(lp_model, coeff_storage[i, ], "<=", rhs_storage[i])
}
```

#Add same capacity percentage constraint
```{r}
for (i in 1:2) {
  add.constraint(lp_model, coeff_percentage[i, ], "=", 0)
}
```

#Solve the LP model
```{r}
solve(lp_model)
optimal_solution <- get.variables(lp_model)
optimal_solution
```
